Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-06-30 sports_analytics.Rmd
started on epv for continuous sports

Even in sports where the concept of a state is not so easy to define, like basketball, the value of a possession can be estimated with player tracking data [@cervone2016multiresolution].

@@

@@

@decroos2019playeraction Actions Speak Louder than Goals: Valuing Player Actions in Soccer

@@

Table \ref{tab:tennisbtm} shows the estimated coefficients of the fitted BTM. According to the abilities, the players are ranked as follows: 1) Djokovic, 2) Federer, 3) Wawrinka, 4) Murray, 5) Nadal. To obtain win probability, as an illustration, for the Federer-Nadal matchup, an estimate for the probability of a Federer victory is
$$
\hat\Pi_{24} = \frac{exp(\hat\beta_2 - \hat\beta_4)}{1 + exp(\hat\beta_2 - \hat\beta_4)} = \frac{exp(1.136 + 0.062)}{1 + exp(1.136 + 0.062)} = 0.768
$$

>>>>

Even in sports where the concept of a state is not so easy to define, like basketball, the value of a possession can be estimated with player tracking data. @cervone2016multiresolution introduces expected possession value (EPV), providing a continuous-time estimate of the expected number of points for the offensive team on a given possession using player and ball locations.

@@

@Yurko2020going football

@@

(These papers shared the same definitions of EPV)

@@

Table \ref{tab:tennisbtm} shows the estimated coefficients of the fitted BTM. According to the abilities, the players are ranked as follows: 1) Djokovic, 2) Federer, 3) Wawrinka, 4) Nadal, 5) Murray To obtain win probability, as an illustration, for the Federer-Nadal matchup, an estimate for the probability of a Federer victory is
$$
\hat\Pi_{24} = \frac{exp(\hat\beta_2 - \hat\beta_4)}{1 + exp(\hat\beta_2 - \hat\beta_4)} = \frac{exp(1.136 + 0.062)}{1 + exp(1.136 + 0.062)} = 0.768
$$
